---
title: "GAE4: Regression"
author: "Your Name Here"
format: 
  html:
    embed-resources: true
    toc: true
    code-tools: true

csl: ecology.csl

editor: visual
bibliography: references.bib
---

```{r}
#| label: SetUp
#| message: FALSE
#| echo: FALSE

knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE
  ) 

library(car)
library(ggfortify)
library(patchwork)
library(broom)
library(latex2exp)       
library(kableExtra)
library(tidyverse)

options(knitr.kable.NA = '')
```

<!--# This chunk is a work-around to allow left-aligned table captions -->

```{=html}
<style type="text/css">
caption, .table-caption {
  text-align: left;
}
</style>
```
# Scenario 1: Does littoral coarse woody debris depend on riparian tree density?

@Christiansen.etal1996 studied the relationships between coarse woody debris (CWD) found in the littoral zone of the lakes and shoreline vegetation in a sample of 16 lakes along the border between northern Wisconsin and the upper-peninsula of Michigan. Coarse woody debris is an important habitat feature for many littoral zone fishes as well as for macroinvertebrates and periphyton.

## Methods

The lakes were chosen to span a range of lake development (density of lake shore cabins). They sampled riparian vegetation and CWD abundance on a total of 125 plots at the 16 survey lakes. Within each plot, all live, and standing dead trees (snags) \>5 cm DBH were identified to species and measured for stem diameter. At the same sites, a 40-m line transect (30 m on developed lakes) was established in the water along the 0.5 m depth contour. All CWD \>5 cm in diameter that intersected the line transect was measured. CWD that did not intersect the 0.5 contour was not counted.

```{r importChrist}
christ <- read_csv(
  "christ.csv",
  comment = "#",
  show_col_types = FALSE
  )

# Using tolower() to force all variables names to lower case.
names(christ) <- tolower(names(christ))

# Remember to have a look at the data.frame in the Environment pane to 
# familiarize yourself with the data. You may also want to open the 
# .csv file in Excel to see how the variables are defined using
# comments.
```

### Statistical Methods

<!-- In this scenario, test for a relationship between CWD and riparian     -->

<!-- tree density. Then describe the relationship.                          -->

<!-- Your statistical methods should be written below these comments.       -->

## Results

<!-- Your code that generates your results could go here along with your    -->

<!-- interpretation of those results. Don't forget to check on assumptions. -->

<!-- Note that while you should check on the assumptions, we very rarely    -->

<!-- include those analyses in the published report.                        -->

# Scenario 2: Does development affect CWD abundance?

The researchers in this study were particularly interested in how shoreline development may have affected coarse woody debris [@Christiansen.etal1996].

## Methods

See methods described above.

### Statistical Methods

<!-- In this scenario, expand on your previous analysis to include the      -->

<!-- effects of cabin density and lake area.                                -->

<!-- In addition to checking the usual diagnostics, remember to look for    -->

<!-- colinearity.                                                           -->

## Results

# References
